\section{Data}
\label{sec:data}

\begin{description}
	\item[Music representation] Which one to choose.
	
	\begin{description}
		\item[Sound waves] frequencies and durations.
		\item[Music notation] notes (pitch, duration) and rests (duration).
		Compressed format of sound waves. Like sound to text.
		\item[Sound spiral] angle (pitch in an octave), octave, duration.
		\item[Others] \dots
	\end{description}
	
	\item[Data set] Nottingham Music Database in ABC format
	
	\begin{itemize}
		\item Nine collections: Jigs, hornpipes, Morris, Playford, reels, slip jigs, waltzes, Christmas, Ashover.
		\item 1034 folk tunes.
		
		\begin{itemize}
			\item 659 in training set (64 \%)
			\item 165 in validation set (16 \%)
			\item 207 in test set (20 \%)
			\item 3 omitted due to bad formatting
		\end{itemize}
		
		\item Example snippet of ABC format.
	\end{itemize}
	
	\item[Features] Preprocessing.
	
	\begin{description}
		\item[Conversion] to notes and rests.
		\item[Extraction] of pitch and durations.
		\item[One-hot encoding] 35 pitch values, 14 duration values, 490 combinations
plus one end-of-sequence character.
	\end{description}
	
	\item[Comparison to EHR] Electronic health records are can be encoded as one- or multi-hit encoding of
	
	\begin{itemize}
		\item diagnosis codes and medicine codes at a visit,
		\item duration between visits.
	\end{itemize}
\end{description}

\subsection*{EHR synopsis}

We use EHR from the Danish National Patient Register (`Landspatientregister' or LPR) and questionnaires from the Danish National Birth Cohort (`Bedre Sundhed for Mor og Barn' or BSMB) provided by SSI in ICD--10 diagnosis codes.
